Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-04-19 sections0.0/results0.0.tex
Updates from ShareLaTeX

            %add more about why Sc is acting differently
            %\import{~/images/texes/}{1by2_t.tex}
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/dist_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by2T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/hit_t_1_by_2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by2Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts. Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/dist_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/hit_t_1_by_3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts. However, this time 2 of galaxies (SB5, and SB6) are separated star bursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes when with increasing the size of map, program pays more attention to small differences between each groups.
            Higher the size of the maps means that even considering the smallest differences between galaxies.
            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 each node).
            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together, respectively. 
            The SB3 and SB4 grouping breaks when we increased the size of the map to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E does not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images/1d/apps/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../images/1d/apps/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{Results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*}

@@

        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in the Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1 \times 2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the SEDs galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These are the similar ones sit on the left node in the upper plot in the Fig.~\ref{fig: 1by2T}.
            The plots clearly shows the 4000\AA~break in the SEDs, which is the one of the signatures of the SED of the early type galaxies.
            The strong the emission line in that figure comes from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of the Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.55\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96. Up: Numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. the left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to divided to two groups, for any SED between these two groups the SOM decides that the galaxy belongs to which group based on the strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve problem of the galaxies which have features of both groups.

@@

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.55\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times3$ to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size we could see, the K96 galaxies separated in 12 different neurons.
            B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of the Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images/1d/hit_v_1_by_22.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times22$ to classify the sample galaxies.}
                \label{fig: 1by22V}
            \end{figure*}
            And the lower plot of the figure represents the average SED of the galaxies in each neurons.
            However, this time, since galaxies had more space to separated some of the neurons left empty. 
            Thus instead of having 22 average SED plots in the lower part of the Fig.~\ref{fig: 1by22V}, we have 12 SEDs.

@@

        \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_2.png}
            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by2V}}
            \label{fig: prop1by2}
        \end{figure}

                \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
            \label{fig: prop1by3}
        \end{figure}

                \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
            \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
            \label{fig: prop1by22}
        \end{figure}

        Figs.~\ref{fig: prop1by2} to ~\ref{fig: prop1by22} show the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
        In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.

        In Fig.~\ref{fig: prop1by2}, from early type galaxies to star burst ones, stellar mass and age decreases while SSFR and $f_\mathrm{burst}$ increases. 
        The same trend is noticeable in both Fig.~\ref{fig: prop1by3} and Fig.~\ref{fig: prop1by22}. 
        The gaps in the Fig.~\ref{fig: prop1by22} is due to the empty neurons in Fig.~\ref{fig: 1by22V}. These trends are another evidence that this method is working properly and can be used to categorized galaxies based on their SEDs or even their physical properties.

@@

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of training network in $12\times12$~grid, when we considered that there are only 12 types of SEDs for galaxies.}
        \label{fig: 12by12T_newsom}
    \end{figure}
    Fig.~\ref{fig: 12by12T_newsom} shows the SOM results for the first approach. 
    Since we considered that SEDs of all galaxies can be categorized using the K96 model, the galaxies took place all over the map.
    Using this network to categorize any set of SEDs, forced the SEDs to be in the same neurons as the K96 ones or the neurons between them.
    However, all the K96 galaxies are in small side of the map in Fig.~\ref{fig: 12by12T_selforg}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even it is way far away from the K96 samples.
    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/2d/dist_12_by_self_org_res12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images/2d/hit_t_12_by_self_org_res12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of training network in $12\times12$~grid, when we considered that there might be some outlier or other type of SEDs.}
        \label{fig: 12by12T_selforg}
    \end{figure}

@@

       \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images/2d/hit_v_12_by_self_org_res12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of categorizing T12 galaxies using $12\times12$~network. Up: categorizing with network shown in Fig.~\ref{fig: 12by12T_newsom}. Down: using network in Fig.~\ref{fig: 12by12T_selforg}.}
        \label{fig: 12by12V}
    \end{figure}

>>>>

            %add more about why Sc is acting differently
            %\import{~/images/texes/}{1by2_t.tex}
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by2T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by2Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts. Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts. However, this time 2 of galaxies (SB5, and SB6) are separated star bursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes when with increasing the size of map, program pays more attention to small differences between each groups.
            Higher the size of the maps means that even considering the smallest differences between galaxies.
            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 each node).
            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together, respectively. 
            The SB3 and SB4 grouping breaks when we increased the size of the map to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E does not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{Results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*}

@@

        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in the Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1 \times 2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the SEDs galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These are the similar ones sit on the left node in the upper plot in the Fig.~\ref{fig: 1by2T}.
            The plots clearly shows the 4000\AA~break in the SEDs, which is the one of the signatures of the SED of the early type galaxies.
            The strong the emission line in that figure comes from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of the Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies from K96. Up: Numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. the left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to divided to two groups, for any SED between these two groups the SOM decides that the galaxy belongs to which group based on the strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve problem of the galaxies which have features of both groups.

@@

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_3.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by3.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times3$ to classify the sample galaxies.}
                \label{fig: 1by3V}
            \end{figure}

            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size we could see, the K96 galaxies separated in 12 different neurons.
            B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of the Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but this time we used network with size of $1\times22$ to classify the sample galaxies.}
                \label{fig: 1by22V}
            \end{figure*}
            And the lower plot of the figure represents the average SED of the galaxies in each neurons.
            However, this time, since galaxies had more space to separated some of the neurons left empty. 
            Thus instead of having 22 average SED plots in the lower part of the Fig.~\ref{fig: 1by22V}, we have 12 SEDs.

@@

        \begin{figure*}
            \centering
            \includegraphics[width=\textwidth]{../images0.01/1d/props3.png}
            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
            \label{fig: props}
        \end{figure*}

        %         \begin{figure}
        %     \centering
        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_3.png}
        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by3V}}
        %     \label{fig: prop1by3}
        % \end{figure}

        %         \begin{figure}
        %     \centering
        %     \includegraphics[width=0.5\textwidth]{../images/1d/prop1_by_22.png}
        %     \caption{Comparing the median of four propertied of galaxies in each nod of Fig.~\ref{fig: 1by22V}}
        %     \label{fig: prop1by22}
        % \end{figure}

        Fig.~\ref{fig: props} shows the results of median of stellar mass, age, specific star formation rate (SSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each nodes in the upper maps of the Figs.~\ref{fig: 1by2V} to ~\ref{fig: 1by22V}.
        In all the plots $x$-axis shows the number of the neurons from left to right, and $y$-axis shows one of the mentioned properties.

        In Fig.~\ref{fig: props}, from early type galaxies to star burst ones, stellar mass and age decreases while SSFR and $f_\mathrm{burst}$ increases, in all three lines. 
        These trends are another evidence that this method is working properly and can be used to categorized galaxies based on their SEDs or even their physical properties.

@@

    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/2d/hit_t_12_by_12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of training network in $12\times12$~grid, when we considered that there are only 12 types of SEDs for galaxies.}
        \label{fig: 12by12T_newsom}
    \end{figure}
    Fig.~\ref{fig: 12by12T_newsom} shows the SOM results for the first approach. 
    Since we considered that SEDs of all galaxies can be categorized using the K96 model, the galaxies took place all over the map.
    Using this network to categorize any set of SEDs, forced the SEDs to be in the same neurons as the K96 ones or the neurons between them.
    However, all the K96 galaxies are in small side of the map in Fig.~\ref{fig: 12by12T_selforg}, which provide enough freedom for SED of the galaxies to take place everywhere in the map even it is way far away from the K96 samples.
    \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images0.01/2d/dist_12_by_self_org_res12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/2d/hit_t_12_by_self_org_res12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of training network in $12\times12$~grid, when we considered that there might be some outlier or other type of SEDs.}
        \label{fig: 12by12T_selforg}
    \end{figure}

@@

       \begin{figure}
        \begin{subfigure}[b]{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_12.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.5\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/2d/hit_v_12_by_self_org_res12.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
        \end{subfigure}
        \caption{Results of categorizing T12 galaxies using $12\times12$~network. Up: categorizing with network shown in Fig.~\ref{fig: 12by12T_newsom}. Down: using network in Fig.~\ref{fig: 12by12T_selforg}.}
        \label{fig: 12by12V}
    \end{figure}

### 2016-04-19 sections0.01/method0.01.tex
Updates from ShareLaTeX

     To show our results, we combine two of the {\tiny NNT}'s built-in plots. 
     A Hits map, which shows number of hits for each neurons, and a distances map, which shows the same neurons as the hits map and the distance between them. 
     To combine these two maps, we wrote number of hits in each neurons in the neurons in a distance map.
     The neurons with zero hit, left empty.
     In distance maps, the grey hexagonal shape areas represent the neurons.
     The red lines between neurons, show the immediate neighbours.
     The distances in a distance map are showing by colours.
     The darker colour represents the larger distance between neurons; whilst the lighter colours means there is small distance between neurons.

@@

 %using self organizing maps instead of the newsom

>>>>

     To show our results, we combine two of the {\tiny NNT}'s built-in plots. 
     A Hits map, which shows number of hits for each neurons, and a distances map, which shows the same neurons as the hits map and the distance between them. 
     %To combine these two maps, we wrote number of hits in each neurons in the neurons in a distance map.
     In the maps, the purple hexagonal shape areas represent the neurons.
     %The red lines between neurons, show the immediate neighbours.
     The distances in a distance map are showing by colours.
     The darker colour represents the larger distance between neurons; whilst the lighter colours means there is small distance between neurons.
     In hit maps, neurons with zero hit left empty.

@@

\subsection{Mock sample}

         \begin{figure}
            \begin{subfigure}[b]{0.5\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/sample/sample2_dist.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{../images0.01/sample/sample2_hits.png}
            \end{subfigure}
            \caption{SOM of the mock sample. In both plots axis shows the position of the neurones. Hexagonal shapes represent the neurons. The upper plot is a distance map. The gray cycle colours shows the differences between weight of each neuron with withe is the minimum differences and black has the maximum one. The lower plot is a hit plot. It represents number of samples in each neurons, while the empty with neurons means zero hit. In this sample the 27 galaxies clustered in 4 groups of 8, 7, 6 and 6 galaxies.}
            \label{fig: sample}
        \end{figure}

 We created  a mock sample of 27 galaxies to illustrate the results of SOMs and how they can be analyzed, and to show how this method works.
 The mock sample contains two information from each galaxy; first type of galaxies: type 1 or type 2, and either they are high or low star forming galaxies.
 We generated a SOM with size of $10 \times 10$ using the same initial values mentioned in the Section ~\ref{sec: create_som}.

 Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
 The upper plot is a distance map. 
 The axis show the position of the neurons in a $10 \times 10$ network. 
 The purple hexagons are illustration of the neurons, and the colours of the area between neighbours are showing the differences between weight of each two neurons.
 In distance maps colour white between neurons represents the minimum value of the differences between weights of neurons and the colour black shows the maximum values. 
 The gray cycle colour between white and black shows values between minimum and maximum with darker colour means more differences.

 The lower plot in the Fig.~\ref{fig: sample} shows a hit map.
 In this map similar to the distance map the axis shows the position of the neurons where the hexagonal shapes are neurons.
 %White neurons show the empty neurons.
 The purple neurons with a number on them shows the number of galaxy in that neurons.
 Colour coverage of neurons is different and depends on the number of the hits on the sample.
 The neuron with the maximum number of hits is completely coloured while the empty neurons are white.

Using this method, as we predicted, we were able to divide the mock sample galaxies in 4 distinct groups: Type 1 with high SFR, type 1 with low SFR, type 2 with high SFR and type 2 with low SFR. 
The upper plot in the Fig.~\ref{fig: sample}, clearly shows this division.
The upper part of the plot are high star forming galaxies, while the lower part of it belongs to the low star forming galaxies.
The left part of the plots is where type 1 galaxies belong to and the right side is for type 2 galaxies.
Grey to black colours shows the border between regions.
The lower plot in Fig.~\ref{fig: sample} shows only 4 neurons out of 100 were occupied. 
8 galaxies are type 1 galaxies with high SFR, 7 are type 2 galaxies with high SFR, 6 are type 1 galaxies with low SFR and the other 6 are type 2 galaxies with low SFR. 
The reason of that there are only 4 filled neurons in the network is the simplicity of the input data, and the fact that each entry only could get either 0 or 1 as for type of galaxy and 0 or 0.5 as an indicator of SFR.
It shows us although each galaxy had enough space to occupy any of the neurons in the network, because of the similarity of values they stayed in only four groups.

As we see in the following sections, In the real world with the real data, we never have two galaxies with exactly the same information.
Therefore, if we gave them enough space they would eventually separate from each other to smaller and smaller groups. 
However, if the  the number of neurons are maaaaauch higher than number of input samples, it shows the input data are pretty similar to each other.
